Residence time, a master variable of ecology, physiology, and natural selection

### 2015-08-27 analyses/2015_06_27_ResTime.Rmd
modified model, ran over night, added results figs -KL

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
## Load Data
sim.data <- read.csv("~/GitHub/hydrobide/results/simulated_data/2015_August/12_Aug/SimData.csv")  
#sim.data <- subset(sim.data, motion == ' random_walk ')
```

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
## Assign Data
sim <- sim.data$sim # the specific simulation run
height <- sim.data$Height
width <- sim.data$Width
flow.rate <- sim.data$FlowRate
seed <- sim.data$starting.seed

@@

N <- sim.data$N
S <- sim.data$S
e.var <- sim.data$e.var
e.simp <- sim.data$simpson.e
avg.ab <- N/S
Skew <-sim.data$skew
Nmax <- sim.data$N.max
SimpD <- sim.data$SD
Whittaker.turnover <- sim.data$species.turnover

@@

sim.data$N[sim.data$N<=0] <- 1
sim.data$N[sim.data$S<=0] <- 1

@@

p1 <- ggplot(data=NULL, aes(x=xs, y=ys)) +
  geom_point(colour="magenta") +
  labs(x= expression(tau), y="Growth") +
  labs(title="Growth rate") +
  scale_x_log10() +
  coord_fixed(ratio = 5.3) +
  theme_black()

maint <- (S*sim.data$avg.per.capita.maint)/N

p2 <- ggplot(data=NULL, aes(x=h.tau, y=maint)) +
  geom_point(colour="cyan") +
  labs(x= expression(tau), y="Maintenance") +
  labs(title="Maintenance") +
  scale_x_log10() +
  scale_y_log10() +
  coord_fixed(ratio = 0.34) +
  theme_black()

>>>>

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
## Load Data
sim.data <- read.csv("~/GitHub/hydrobide/results/simulated_data/2015_August/25_Aug/SimData.csv")  
#sim.data <- subset(sim.data, motion == ' random_walk ')
```

```{r, results = 'hide', echo=FALSE, message = FALSE, warning = FALSE}
## Assign Data
sim <- sim.data$sim # the specific simulation run
height <- sim.data$height
width <- sim.data$width
flow.rate <- sim.data$flow.rate
seed <- sim.data$starting.seed

@@

N <- sim.data$total.abundance
S <- sim.data$species.richness
e.var <- sim.data$e.var
e.simp <- sim.data$simpson.e
avg.ab <- N/S
Skew <-sim.data$skew
Nmax <- sim.data$N.max
SimpD <- sim.data$SD
Whittaker.turnover <- sim.data$species.turnover

res.inflow <- sim.data$res.inflow
N.res.types <- sim.data$N.res.types
P.res.types <- sim.data$P.res.types
C.res.types <- sim.data$C.res.types
max.res.val <- sim.data$max.res.val

res.conc <- sim.data$resource.concentration
num.tracers <- sim.data$tracer.particles
num.resources <- sim.data$resource.particles

biomass.prod.N <- sim.data$biomass.prod.N
biomass.prod.P <- sim.data$biomass.prod.P
biomass.prod.C <- sim.data$biomass.prod.C
```

@@

sim.data$total.abundance[sim.data$total.abundance<=0] <- 1
N[N<=0] <- 1
sim.data$species.richness[sim.data$species.richness<=0] <- 1
S[S<=0] <- 1

@@

p1 <- ggplot(data=NULL, aes(x=xs, y=ys)) +
  geom_point(colour="magenta") +
  labs(x= expression(tau), y="Growth") +
  labs(title="Growth rate") +
  scale_x_log10() +
  coord_fixed(ratio = 100) +
  theme_black()

#maint <- (S*sim.data$avg.per.capita.maint)/N
maint <- sim.data$avg.per.capita.maint

p2 <- ggplot(data=NULL, aes(x=h.tau, y=maint)) +
  geom_point(colour="cyan") +
  labs(x= expression(tau), y="Maintenance") +
  labs(title="Maintenance") +
  scale_x_log10() +
  scale_y_log10() +
  coord_fixed(ratio = 8) +
  theme_black()
